Microscopy Data

### 2019-06-20 Microscopy Data.Rmd
finished functions for aggregate sizes

testFile2<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t00_p1.csv"

GetAggregates<-function(sample){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))}}
return(growthDf)
}

@@

testReadAggregateFile<-ReadAggregateFile(tes)
```
You can also embed plots, for example:

>>>>

testAggFile1<-"/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/3-13-19/aggregateSizes/t_00p_1.csv"

GetAggregates<-function(sample){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/Spatial paper Data/Microscopy Data/Other Data/',sample,'/aggregateSizes')
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p_",position,"."),fileList)]
    for (timepoint in 0:17){

      currentTimePoint<-currentPosition[grep(paste0("t_",GetNumber(timepoint),"p_"),currentPosition)]

      growthDf<-rbind(growthDf,ReadAggregateFile(currentTimePoint, position, timepoint))

      }
    }
return(growthDf)
}

testGetAggregates<- GetAggregates("3-13-19")

@@

testReadAggregateFile<-ReadAggregateFile(testAggFile1, 1 ,2)
```
You can also embed plots, for example:
